\documentclass[oneside,a4paper,parskip=half]{scrartcl}
%Anpassbare Enumerates/Itemizes
\usepackage{enumitem}
\usepackage{color}
\usepackage{libertine}

\newcommand{\ra}{\ensuremath{\rightarrow}}
\newcommand{\Ra}{\ensuremath{\Rightarrow}}
\begin{document}
\section*{How should you write technical documents}
\begin{enumerate}
\item Impersonal
		\begin{itemize}[label=\ra]
		\item Do not use ``I'', do not use ``you''
		\item If a human agent is part of the process, then the function is used e.g. ``the user'', ``the operator'', ``the administrator'', ``the programmer'' etc.
		\end{itemize}

\item High level specialist vocabulary
		\begin{itemize}[label=\ra]
		\item no slang
		\item no ``everyday'' vocabulary where specialist terms are available
		\item technical terms must be repeated if it is not possible to use a pronoun
				\begin{itemize}[label=\Ra]
				\item do not use different words for style reason
				\end{itemize}
		\end{itemize}

\item Objective
		\begin{itemize}[label=\ra]
		\item no personal opinions
		\item no emotional language
		\end{itemize}

\item There is much greater use of passive verb structures in specialist texts than in ``everyday'' language.
		\begin{itemize}[label=\ra]
		\item the passive focuses more clearly on what is being described
		\item it avoids overloading the text with superfluous information that distracts the reader from the focus
		\end{itemize}

\item Conventionally, short forms are not used in formal writing - \textbf{No} ``don't, doesn't, isn't'' et cetera. Always use ``do not, does not,'' and so on.
\item The content of the text must be logically structured. The reader must always be able to recognize a thread and follow it.
\item Professional technical texts are \textbf{not} ``Stilaufsätze''
\end{enumerate}

\begin{description}
\item[Task] Describe the main features of MS Word (200 Words)
\end{description}
\textcolor{red}{How \underline{NOT} to do it!}\\
Nowadays, it is  difficult to imagine an office environment in which computers are not used for carrying out routine tasks. Over the years, one product has established itself as the market leader in the field of office word processing applications. This product is MS Word.

\textcolor{green}{How to do it}\\
The most useful feature of MS word is\dots
\end{document}
